Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-17 write_up/F_changes.tex
All revisions to figures

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Tue Feb 19 17:00:17 2019
\begin{longtable}{rllrrrlllr}
\caption{Fishing mortality effects of the
     closure scenarios (ordered by most effective first)} \\ 
  \hline
scenario & metric & pop & before & after & diff & timescale & basis & data\_type & resolution \\ 
  \hline
  9 & F & spp\_3 & 1.08 & 0.29 & -73.47 & weekly & high\_pop & real\_pop & 1.00 \\ 
   10 & F & spp\_3 & 1.08 & 0.29 & -72.94 & monthly & high\_pop & real\_pop & 1.00 \\ 
   11 & F & spp\_3 & 1.08 & 0.35 & -68.04 & yearly & high\_pop & real\_pop & 1.00 \\ 
   45 & F & spp\_3 & 1.08 & 0.58 & -46.70 & yearly & high\_pop & commercial & 20.00 \\ 
    1 & F & spp\_3 & 1.08 & 0.58 & -46.21 & weekly & high\_pop & commercial & 1.00 \\ 
   23 & F & spp\_3 & 1.08 & 0.59 & -45.27 & weekly & high\_pop & real\_pop & 5.00 \\ 
    2 & F & spp\_3 & 1.08 & 0.59 & -45.06 & monthly & high\_pop & commercial & 1.00 \\ 
    7 & F & spp\_3 & 1.08 & 0.60 & -44.48 & yearly & high\_pop & survey & 1.00 \\ 
   24 & F & spp\_3 & 1.08 & 0.61 & -43.20 & monthly & high\_pop & real\_pop & 5.00 \\ 
    3 & F & spp\_3 & 1.08 & 0.64 & -40.82 & yearly & high\_pop & commercial & 1.00 \\ 
   25 & F & spp\_3 & 1.08 & 0.65 & -39.94 & yearly & high\_pop & real\_pop & 5.00 \\ 
   17 & F & spp\_3 & 1.08 & 0.67 & -38.11 & yearly & high\_pop & commercial & 5.00 \\ 
   15 & F & spp\_3 & 1.08 & 0.71 & -34.38 & weekly & high\_pop & commercial & 5.00 \\ 
   43 & F & spp\_3 & 1.08 & 0.71 & -34.31 & weekly & high\_pop & commercial & 20.00 \\ 
   16 & F & spp\_3 & 1.08 & 0.73 & -32.58 & monthly & high\_pop & commercial & 5.00 \\ 
   51 & F & spp\_3 & 1.08 & 0.78 & -27.92 & weekly & high\_pop & real\_pop & 20.00 \\ 
   37 & F & spp\_3 & 1.08 & 0.78 & -27.76 & weekly & high\_pop & real\_pop & 10.00 \\ 
   39 & F & spp\_3 & 1.08 & 0.79 & -26.98 & yearly & high\_pop & real\_pop & 10.00 \\ 
   38 & F & spp\_3 & 1.08 & 0.81 & -25.47 & monthly & high\_pop & real\_pop & 10.00 \\ 
   21 & F & spp\_3 & 1.08 & 0.81 & -25.21 & yearly & high\_pop & survey & 5.00 \\ 
   35 & F & spp\_3 & 1.08 & 0.81 & -25.05 & yearly & high\_pop & survey & 10.00 \\ 
   44 & F & spp\_3 & 1.08 & 0.87 & -19.91 & monthly & high\_pop & commercial & 20.00 \\ 
   52 & F & spp\_3 & 1.08 & 0.88 & -18.39 & monthly & high\_pop & real\_pop & 20.00 \\ 
   30 & F & spp\_3 & 1.08 & 0.96 & -11.06 & monthly & high\_pop & commercial & 10.00 \\ 
   29 & F & spp\_3 & 1.08 & 0.98 & -9.80 & weekly & high\_pop & commercial & 10.00 \\ 
   31 & F & spp\_3 & 1.08 & 1.03 & -4.36 & yearly & high\_pop & commercial & 10.00 \\ 
   53 & F & spp\_3 & 1.08 & 1.06 & -1.64 & yearly & high\_pop & real\_pop & 20.00 \\ 
   49 & F & spp\_3 & 1.08 & 1.07 & -1.01 & yearly & high\_pop & survey & 20.00 \\ 
   \hline
\hline
\label{tab:6}
\end{longtable}

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Tue Sep 17 17:32:36 2019
\begin{longtable}{rlrrrllr}
\caption{Fishing mortality effects of the
	     closure scenarios (ordered by most effective first)} \\ 
  \hline
Scenario No & Population & F before & F after & \% F change & data type & timescale & resolution \\ 
  \hline
  9 & Population 3 & 1.08 & 0.29 & -73.47 & True Population & weekly & 1.00 \\ 
   10 & Population 3 & 1.08 & 0.29 & -72.94 & True Population & monthly & 1.00 \\ 
   11 & Population 3 & 1.08 & 0.35 & -68.04 & True Population & yearly & 1.00 \\ 
   45 & Population 3 & 1.08 & 0.58 & -46.70 & commercial & yearly & 20.00 \\ 
    1 & Population 3 & 1.08 & 0.58 & -46.21 & commercial & weekly & 1.00 \\ 
   23 & Population 3 & 1.08 & 0.59 & -45.27 & True Population & weekly & 5.00 \\ 
    2 & Population 3 & 1.08 & 0.59 & -45.06 & commercial & monthly & 1.00 \\ 
    7 & Population 3 & 1.08 & 0.60 & -44.48 & survey & yearly & 1.00 \\ 
   24 & Population 3 & 1.08 & 0.61 & -43.20 & True Population & monthly & 5.00 \\ 
    3 & Population 3 & 1.08 & 0.64 & -40.82 & commercial & yearly & 1.00 \\ 
   25 & Population 3 & 1.08 & 0.65 & -39.94 & True Population & yearly & 5.00 \\ 
   17 & Population 3 & 1.08 & 0.67 & -38.11 & commercial & yearly & 5.00 \\ 
   15 & Population 3 & 1.08 & 0.71 & -34.38 & commercial & weekly & 5.00 \\ 
   43 & Population 3 & 1.08 & 0.71 & -34.31 & commercial & weekly & 20.00 \\ 
   16 & Population 3 & 1.08 & 0.73 & -32.58 & commercial & monthly & 5.00 \\ 
   51 & Population 3 & 1.08 & 0.78 & -27.92 & True Population & weekly & 20.00 \\ 
   37 & Population 3 & 1.08 & 0.78 & -27.76 & True Population & weekly & 10.00 \\ 
   39 & Population 3 & 1.08 & 0.79 & -26.98 & True Population & yearly & 10.00 \\ 
   38 & Population 3 & 1.08 & 0.81 & -25.47 & True Population & monthly & 10.00 \\ 
   21 & Population 3 & 1.08 & 0.81 & -25.21 & survey & yearly & 5.00 \\ 
   35 & Population 3 & 1.08 & 0.81 & -25.05 & survey & yearly & 10.00 \\ 
   44 & Population 3 & 1.08 & 0.87 & -19.91 & commercial & monthly & 20.00 \\ 
   52 & Population 3 & 1.08 & 0.88 & -18.39 & True Population & monthly & 20.00 \\ 
   30 & Population 3 & 1.08 & 0.96 & -11.06 & commercial & monthly & 10.00 \\ 
   29 & Population 3 & 1.08 & 0.98 & -9.80 & commercial & weekly & 10.00 \\ 
   31 & Population 3 & 1.08 & 1.03 & -4.36 & commercial & yearly & 10.00 \\ 
   53 & Population 3 & 1.08 & 1.06 & -1.64 & True Population & yearly & 20.00 \\ 
   49 & Population 3 & 1.08 & 1.07 & -1.01 & survey & yearly & 20.00 \\ 
   \hline
\hline
\label{tab:6}
\end{longtable}

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
All revisions to figures

\usepackage{hhline}
\usepackage{booktabs}
%\usepackage[textsize=scriptsize]{todonotes}
\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
\usepackage{eurosym}
\usepackage{longtable}

@@

To answer this question we compare different spatial and temporal aggregations
of the real population distributions to:
\begin{enumerate}[label=\alph*)]
	\item \textbf{fisheries-independent data:} the inferred population from
		a fixed-site sampling survey design as commonly used for
		fisheries monitoring purposes;
	\item \textbf{fisheries-dependent data:} the inferred population from
		our fleet model that includes fishery-induced sampling
		dynamics.
\end{enumerate}

We allow the simulation to run unrestricted for 30 years, then implement
spatial closed areas for the last 20 years of the simulation based on data
(either derived from the commercial catches, fisheries-independent survey or
the real population used at different spatial and temporal scales. \\

@@

\begin{enumerate}
	\item Extract data source (real population, commercial or survey), 
	\item Aggregate according to desired spatial and temporal resolution,
	\item Interpolate across entire area at desired resolution using simple
		bivariate interpolation using the \emph{interp} function from
		the R package akima \citep{Akima2006}. This is intended to
		represent a naive spatial model of catch rates, without
		knowledge of the spatial population dynamics.
	\item Close area covering top 5 \% of catch rates 
\end{enumerate}
In total 28 closure scenarios were run that represent combinations of:

\begin{itemize}
	\item \textbf{data types:} commercial logbook data, survey data and
		real population,
	\item \textbf{temporal resolutions:} weekly, monthly and yearly
		closures,
	\item \textbf{spatial resolutions:} 1 x 1 grid, 5 x 5 grid, 10 x 10
		grid and 20 x 20 grid,
	\item \textbf{closure basis:} highest 5 \%  of catch rates for the
		protected species
\end{itemize}

@@

The aggregated catch composition from each of the data sources over a ten-year
period (which shows average seasonal patterns) at different spatial resolutions
highlights different patterns in perceived community structure depending on the
data source and aggregation level (Figure \ref{fig:1}). The finer spatial grid
for the real population (top left) and commercial data (top middle) show
visually similar patterns, though there are large unsampled areas in the
commercial data from a lack of fishing activity (particularly in the lower left
part of the sampling domain). The survey data at this spatial resolution
displays very sparse information about the spatial distributions of the
populations. The slightly aggregated data on a 5 x 5 grid shows similar
patterns and, while losing some of the spatial detail, there remains good
consistency between the real population and the commercial data. Survey data
starts to pick out some of the similar patterns as the other data sources, but
lacks spatiotemporal coverage. The spatial catch information on a 10 x 10 and
20 x 20 grid lose a significant amount of information about the spatial
resolutions for all data sources, and some differences between the survey,
commercial and real population data emerge. \\

Different perceptions of the proportion of each stock in an area are seen when
we aggregate the data over a smaller geographical region at different
timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
the real population, the monthly aggregation captures the major patterns of
composition seen in the weekly data with the percentage of different species in
the catch having similar mean and standard deviations.  In the weekly data
species 1 = 9.36 (3.99), species 2 = 83.2 (5.60), species 3 = 3.57 (1.23),
species 4 = 3.91 (1.59); in the monthly data species 1 = 9.23 (3.87), species 2
= 83.3 (5.52), species 3 = 3.62 (1.15), species 4 = 3.86 (1.52). While means
were similar some of the variation was lost when aggregated to an annual level;
species 1 = 9.90 (0.173), species 2 = 82.2 (0.308), species 3 = 3.82 (0.119),
species 4 = 4.03 (0.0502).\\

The commercial data on a weekly basis shows some of the same patterns as the
real population, though the species 1 (in red) is less well represented and
some weeks are missing catches from the area. Here, weekly and monthly
compositions were nearly identical, with monthly composition of species 1 =
0.0472 (0.0139), species 2 = 94.4 (1.47), species 3 = 3.12 (1.47), species 4 =
2.40 (0.444). Again, yearly values head a similar mean but smaller standard
deviation.\\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account (Figures X,Y,Z). \\

Our simulation shows that, despite biases introduced through the fishing
process, the commercially derived data could still inform on the key spatial
patterns in the community structures where the fisheries occurred, which was
spatially limited due to the ``hotspots" of commercially valuable species being
fished. Similarly, despite the even spatial coverage the survey was able to
capture some of the same spatial patterns as the real population, but missed
others due to gaps between survey stations limiting spatial and temporal
coverage (Figures X,Y,Z). This provides a challenge when
modelling unsampled areas in inferring species distribution maps, though these
limitations may be overcome by understanding the relationship between the
species and habitat covariates where these are known at unsampled locations
\citep{Robinson2011}. \\

@@

%% the tikz figure
\clearpage
\input{Process_model.tex}
%\begin{comment}
\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Spatial density (log abundance) for each of the four
		populations at four time steps. The darker the colour the
		greater the density of the population. Note that you can see
		the diagonal isotropic patterns in populations 2 and 3 and
		concentrated spawning areas in the second row of the panels
		(t=18) }
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		across the entire spatial domain showing weekly and seasonal
		patterns in exploitation.  Individual years and the light grey
		lines, the mean of all years the thick black line}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
	\caption{(A) The fishing locations (points) and movements (lines) of a
		single vessel during a trip overlaid on the relative value of a
		fishing site; (B) the fishing locations of the vessel over
		several trips (value field changes over the period so not
		shown). Note that the field is wrapped on a torus so that
		distances between opposite side of the spatial domain are
		considered next to each other, hence apparent large movements;
		(C) the locations of multiple vessels from the same fleet
		overlaid on the value field, (D) the realised step distance and
		turning angles for a single vessel over the simulation}
	\label{fig:mv}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{Data aggregation at different spatial resolutions over a
		ten year period}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev2}
	\caption{Data aggregation at different temporal resolutions over a
		ten-year period}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{Comparison of closure scenarios effect on fishing mortality
		trends. Line colour denotes the timescale, while linestyle
		denotes the spatial resolution. The vertical dashed line
		indicates the onset of the spatial closures.}
	\label{fig:3}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{Closure fishing locations based on annual closures with a
		coarse spatial resolution. Closure location can be seen in red
	in relation to a) before the closure fishing locations, b) after the
	closure fishing locations, c) species 3 habitat distribution}
	\label{fig:17}
\end{figure}	
%\end{comment}

>>>>

\usepackage{hhline}
\usepackage{booktabs}
\usepackage{eurosym}
\usepackage{longtable}

@@

To answer this question we compare different spatial and temporal aggregations
of the true population distributions to:
\begin{enumerate}[label=\alph*)]
	\item \textbf{fisheries-independent data:} the inferred population from
		a fixed-site sampling survey design as commonly used for
		fisheries monitoring purposes;
	\item \textbf{fisheries-dependent data:} the inferred population from
		our fleet model that includes fishery-induced sampling
		dynamics.
\end{enumerate}

We allow the simulation to run unrestricted for 30 years, then implement
spatial closed areas for the last 20 years of the simulation based on data
(either derived from the commercial catches, fisheries-independent survey or
the true population used at different spatial and temporal scales. \\

@@

\begin{enumerate}
	\item Extract data source (true population, commercial or survey), 
	\item Aggregate according to desired spatial and temporal resolution,
	\item Interpolate across entire area at desired resolution using simple
		bivariate interpolation using the \emph{interp} function from
		the R package akima \citep{Akima2006}. This is intended to
		represent a naive spatial model of catch rates, without
		knowledge of the spatial population dynamics.
	\item Close area covering top 5 \% of catch rates 
\end{enumerate}
In total 28 closure scenarios were run that represent combinations of:

\begin{itemize}
	\item \textbf{data types:} commercial logbook data, survey data and
		true population,
	\item \textbf{temporal resolutions:} weekly, monthly and yearly
		closures,
	\item \textbf{spatial resolutions:} 1 x 1 grid, 5 x 5 grid, 10 x 10
		grid and 20 x 20 grid,
	\item \textbf{closure basis:} highest 5 \%  of catch rates for the
		protected species
\end{itemize}

@@

The aggregated catch composition from each of the data sources over a ten-year
period (which shows average seasonal patterns) at different spatial resolutions
highlights different patterns in perceived community structure depending on the
data source and aggregation level (Figure \ref{fig:1}). The finer spatial grid
for the true population (top left) and commercial data (top middle) show
visually similar patterns, though there are large unsampled areas in the
commercial data from a lack of fishing activity (particularly in the lower left
part of the sampling domain). The survey data at this spatial resolution
displays very sparse information about the spatial distributions of the
populations. The slightly aggregated data on a 5 x 5 grid shows similar
patterns and, while losing some of the spatial detail, there remains good
consistency between the true population and the commercial data. Survey data
starts to pick out some of the similar patterns as the other data sources, but
lacks spatiotemporal coverage. The spatial catch information on a 10 x 10 and
20 x 20 grid lose a significant amount of information about the spatial
resolutions for all data sources, and some differences between the survey,
commercial and true population data emerge. \\

Different perceptions of the proportion of each stock in an area are seen when
we aggregate the data over a smaller geographical region at different
timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
the true population, the monthly aggregation captures the major patterns of
composition seen in the weekly data with the percentage of different species in
the catch having similar mean and standard deviations.  In the weekly data
species 1 = 9.36 (3.99), species 2 = 83.2 (5.60), species 3 = 3.57 (1.23),
species 4 = 3.91 (1.59); in the monthly data species 1 = 9.23 (3.87), species 2
= 83.3 (5.52), species 3 = 3.62 (1.15), species 4 = 3.86 (1.52). While means
were similar some of the variation was lost when aggregated to an annual level;
species 1 = 9.90 (0.173), species 2 = 82.2 (0.308), species 3 = 3.82 (0.119),
species 4 = 4.03 (0.0502).\\

The commercial data on a weekly basis shows some of the same patterns as the
true population, though the species 1 (in red) is less well represented and
some weeks are missing catches from the area. Here, weekly and monthly
compositions were nearly identical, with monthly composition of species 1 =
0.0472 (0.0139), species 2 = 94.4 (1.47), species 3 = 3.12 (1.47), species 4 =
2.40 (0.444). Again, yearly values head a similar mean but smaller standard
deviation.\\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account (Figures \ref{fig:9}, \ref{fig:mv}). \\

Our simulation shows that, despite biases introduced through the fishing
process, the commercially derived data could still inform on the key spatial
patterns in the community structures where the fisheries occurred, which was
spatially limited due to the ``hotspots" of commercially valuable species being
fished. Similarly, despite the even spatial coverage the survey was able to
capture some of the same spatial patterns as the true population, but missed
others due to gaps between survey stations limiting spatial and temporal
coverage (Figure \ref{fig:1}). This provides a challenge when
modelling unsampled areas in inferring species distribution maps, though these
limitations may be overcome by understanding the relationship between the
species and habitat covariates where these are known at unsampled locations
\citep{Robinson2011}. \\

@@

%% the tikz figure
\clearpage
\input{Process_model.tex}
%\begin{comment}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Spatial density (log abundance) for each of the four
		populations at four time steps. The darker the colour the
		greater the density of the population. Note that you can see
		the diagonal isotropic patterns in populations 2 and 3 and
		concentrated spawning areas in the second row of the panels
		(t=18).}
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		across the entire spatial domain showing weekly and seasonal
		patterns in exploitation.  Individual years and the light grey
		lines, the mean of all years the thick black line.}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
	\caption{(A) The fishing locations (points) and movements (lines) of a
		single vessel during a trip overlaid on the revenue of a
		fishing site (catch x price); (B) the fishing locations of the
		vessel over several trips (value field changes over the period
		so not shown). Note that the field is wrapped on a torus so
		that distances between opposite side of the spatial domain are
		considered next to each other, hence apparent large movements;
		(C) the locations of multiple vessels from the same fleet
		overlaid on the value field, (D) the realised step distance and
		turning angles for a single vessel over the simulation.}
	\label{fig:mv}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{Data aggregation at different spatial resolutions over a
		ten year period.}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_time_Rev2}
	\caption{Proportion of each population (y axis) for data aggregated at
		different temporal resolutions. Data is aggregated over a
		ten-year period for an area 20 x 20. Each bar represents either
		a week, month or year respectively.}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{Comparison of closure scenarios effect on fishing mortality
		trends. Line colour denotes timescale, while linestyle
		denotes spatial resolution. The vertical dashed line
		indicates the onset of the spatial closures.}
	\label{fig:3}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{Closure fishing locations based on annual closures with a
		coarse spatial resolution. Closure location can be seen in red
	in relation to a) before the closure fishing locations, b) after the
	closure fishing locations, c) species 3 habitat distribution.}
	\label{fig:17}
\end{figure}	
%\end{comment}
